Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Adding details about multiplatform in p.12. Related to #32. Please @JJ @fergunet @pacastillo review before closing

As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}. The first one monitors the environment (context) and the users' behaviour, translating their actions in a sequence of events. These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module. Then, a decision is taken in the corporate Security Operations Centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context. The corresponding feedback is communicated to the user through the \textit{actuator}, who decides to comply or not with the policy. As was mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high. In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease.

The designed MUSES architecture is shown in Figure \ref{fig:architecture}. It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform (operating system and type of device). The \textit{server} side can be installed in the corporate server. Both sides are connected through a secure channel (using HTTPS) over the Internet. In that figure just the high-level components in each part are shown, along with the way the information flows in the system. %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras

>>>>

As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}. The first one monitors the environment (context) and the users' behaviour, translating their actions in a sequence of events. These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module. Then, a decision is taken in the corporate Security Operations Centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context. The corresponding feedback is communicated to the user through the \textit{actuator}, and then the user decides to comply or not with the policy. As was mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high. In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease.

The designed MUSES architecture is shown in Figure \ref{fig:architecture}. It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform. On the one hand, MUSES client has been developed for Android, to be used in Android smartphones and tablets, as well as for Windows, so it can be used in Windows devices and laptops, and finally, iOS client will be also developed. On the other hand, MUSES server has been developed in Java, and works with an Apache Tomcat server. The \textit{server} side can be installed in the corporate server. Both sides are connected through a secure channel (using HTTPS) over the Internet. In that figure just the high-level components in each part are shown, along with the way the information flows in the system. %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras
